Considering scale in multilayer animal social networks

### 2020-06-23 paper/manuscript.Rmd
box 2 edits

# Box 2 
Silk et al. (2018) summarized some key multilayer questions in animal behaviour
research. While these questions are important for linking animal behaviour and
multilayer networks, we summarize our perspectives on the future of multilayer
networks with an additional set of questions posed through the lens of spatial
ecology that are relevant to scale in multilayer networks:

>>>>

# Box 2 
Silk et al. (2018) summarized some key multilayer questions in animal behaviour
research. While these questions are important for linking animal behaviour and
multilayer networks, we pose an additional set of questions on the future of multilayer
networks through the lens of scale and behavioural, landscape, and spatial ecology:
